---
title: "p8105_hw1_nz2333"
author: nz2333
date: 9/28/2021
output: github_document
---

```{r}
library(tidyverse)
```

Problem 1

_Creating data file_

```{r problem1-1}
prbone_df=
  tibble(
    random_sample = rnorm(10),
    random_sample_logic = random_sample > 0,
    character = c("Red", "Orange", "Yellow", "Pink",
                  "Green", "Blue", "White",
                  "Brown", "Grey", "Black"),
    factor_level = factor(c("Light", "Light", "Light", "Light", 
                           "Neutral", "Neutral", "Neutral", 
                           "Dark", "Dark", "Dark"))
  )
```

_Get the mean value_

```{r problem1-2}
mean(pull(prbone_df, var = random_sample))
mean(pull(prbone_df, var = random_sample_logic))
mean(pull(prbone_df, var = character))
mean(pull(prbone_df, var = factor_level))
```

/Based on the results, we can get mean values for the first two variables: random_sample and random_sample_logic. But we were unable to get the mean value for character and factor_level because they are not in numeric or logical format./ 

_Convert to numeric_

```{r problem1-3, results = "hide"}
as.numeric(pull(prbone_df, random_sample_logic))
as.numeric(pull(prbone_df, character))
as.numeric(pull(prbone_df, factor_level))
```

/random_sample_logic and factor_level were successfully converted to numeric forms coded with numbers. But the character variable converted to NA's, because it was not able to convert from character words to numeric numbers. /

/This explains why the mean calculation failed for character variables, becuase they were not being converted to numeric and thus unable to calculate mean value for character variables./

Problem 2

_load dataset_

```{r load data}
data("penguins", package = "palmerpenguins")
```

/The dataset "penguins" has 8 variables: species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. Variables bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, and year are numeric variables. 

It has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 

The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm=T)`./

_Scatter plot_
```{r scatterlot}
ggplot(data = penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species )) + geom_point()

ggsave("Prob2_Scatterplot.png")
```



